Embracing the Laws of Physics: \\ Reversible Models of Computation

### 2017-12-06 survey/survey.tex
add 3 paragraphs to the 'Programs as Reversible Deformations' section.

All programs/proofs/deductions are  
isomorphisms/equivalences/deformations.

>>>>

To better understand conservation of information, we can look
for analogous ideas outside of computing. Turning again to physics,
but this time at the macro scale, what does it mean to transform an
object in such a way that we do not lose the fundamental character
of the object?

For rigid objects (like a chair), the only such transformations are
translations and rotations. But what about something more flexible,
such as a water balloon?  They can be \textbf{deformed} in various ways,
but still retain their fundamental character -- as long as we do not
puncture them or over-stretch them. Ignoring material characteristics
(i.e. over-stretching), what is special about these deformations, as well
as for translations and rotations, is that they correspond to
continuous maps, with a continuous inverse. In fact, even more is
true: they are analytic maps, with analytic inverses. For our purpose,
the most important part is that such maps are infinitely differentiable.
In other words, not only is there an inverse to the deformation, but
its derivative is also invertible, and so on.

When we look around, we find many different words for related
concepts: isomorphism, equivalence, sameness, equality, interchangeability,
comparability, and correspondence, to name a few. Some of these
are informal concepts, while others have formal mathematical meaning.
More important, even amongst the formal concepts, there are differences
-- which is why there are so many of them! Thus we seek a concept
which is neither too strong nor too weak, that will express when
some structured information should be treated as ``the same''.

\jc{wavefront}
All programs/proofs/deductions are  
isomorphisms/equivalences/deformations.
